Title

### 2019-05-07 paper_notes.Rmd
checked function

>>>>

The function below works with the modelization of utility. In @zhang2004, it is assumed people have a preference for mixed neighborhood ($u=1$  at 50%), depending on number of agents in neighborhood. As formulated now, the number of desired agents $n$ is substituted with the desired fraction. The first 3 steps compares to @zhang2004 results, Z = 1 and M = 0.6 the last one is to test with a neighborhood of 6 patches. With $m=0$, utility is constant once the ideal payoff is reached as in a threshold model, with $m=1$, symmetrical peaked function results To edit in table

```{r testing function, echo=FALSE}

f <- function(P,Z,M,x,n){
  if (x/n  <= P){U <- ((x/n)/P)}
  else {U <- (2*Z-M) + (((M-Z)*(x/n))/P)}
  round(U,digits = 3)
 # print(U)
}

f0m <- f(0.5,1,0.6,0,8)
f1m <- f(0.5,1,0.6,1,8)
f2m <- f(0.5,1,0.6,2,8)
f3m <- f(0.5,1,0.6,3,8)
f4m <- f(0.5,1,0.6,4,8)
f5m <- f(0.5,1,0.6,5,8)
f6m <- f(0.5,1,0.6,6,8)
f7m <- f(0.5,1,0.6,7,8)
f8m <- f(0.5,1,0.6,8,8)

utilitym <- c(f0m,f1m,f2m,f3m,f4m,f5m,f6m,f7m,f8m)
concentrationm <- c(0:8)

f0vn <- f(0.5,1,0.6,0,4)
f1vn <- f(0.5,1,0.6,1,4)
f2vn <- f(0.5,1,0.6,2,4)
f3vn <- f(0.5,1,0.6,3,4)
f4vn <- f(0.5,1,0.6,4,4)

utilityvn <- c(f0vn,f1vn,f2vn,f3vn,f4vn)
concentrationvn <- c(0:4)

f0r2 <- f(0.5,1,0.6,0,12)
f1r2 <- f(0.5,1,0.6,1,12)
f2r2 <- f(0.5,1,0.6,2,12)
f3r2 <- f(0.5,1,0.6,3,12)
f4r2 <- f(0.5,1,0.6,4,12)
f5r2 <- f(0.5,1,0.6,5,12)
f6r2 <- f(0.5,1,0.6,6,12)
f7r2 <- f(0.5,1,0.6,7,12)
f8r2 <- f(0.5,1,0.6,8,12)
f9r2 <- f(0.5,1,0.6,9,12)
f10r2 <- f(0.5,1,0.6,10,12)
f11r2 <- f(0.5,1,0.6,11,12)
f12r2 <- f(0.5,1,0.6,12,12)

utilityr2 <- c(f0r2,f1r2,f2r2,f3r2,f4r2,f5r2,f6r2,f7r2,f8r2,f9r2,f10r2,f11r2,f12r2)
concentrationr2 <- c(0:12)

f0t6 <- f(0.5,1,0.6,0,6)
f1t6 <- f(0.5,1,0.6,1,6)
f2t6 <- f(0.5,1,0.6,2,6)
f3t6 <- f(0.5,1,0.6,3,6)
f4t6 <- f(0.5,1,0.6,4,6)
f5t6 <- f(0.5,1,0.6,5,6)
f6t6 <- f(0.5,1,0.6,6,6)

utilityt6 <- c(f0t6,f1t6,f2t6,f3t6,f4t6,f5t6,f6t6)
concentrationt6 <- c(0:6)

print(utilityvn)
plot(concentrationvn,utilityvn)

print(utilitym)
plot(concentrationm,utilitym)

print(utilityr2)
plot(concentrationr2,utilityr2)

print(utilityt6)
plot(concentrationt6,utilityt6)

```
